Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors

### 2019-02-06 paper/ms.tex
Few quick fixes to Carlyn's manuscript. In looking at the new versions of the figures that she and Dean pushed, I realized that the order and text of a couple were swapped. Also fixed a few text things.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}
Thermonuclear (Type Ia) supernovae (\SNeIa) are bright stellar explosions 
thought to occur when approximately 1.X \Msun\ of material composed principally 
of C and O burns under degenerate conditions (SETTLE ON X). This class of supernovae is
know to synthesize much of the Fe-group elements found in the galaxy and
the light curves of these events have a spectial property that allows
their use as distance indicators for cosmological studies~\citep{phillips:absolute}
resulting in the discovery of the acceleration of the expansion of
the Universe and thus the inference of Dark 
Energy~\citep{riess.filippenko.ea:observational,
perlmutter.aldering.ea:measurements,leibundgut2001}. 
This special property of the light curve is thought to follow
from the fact that the source of luminosity, the radioactive decay
of \Ni{56}, synthesized by the thermonuclear burning, is also the
principle source of opacity~\citep{Pinto2001The-type-Ia-sup}.

@@

The single degenerate picture posits a white dwarf gaining mass
from a main-sequence companion. The process relies on a long
period of accretion combined with either steady burning or a 
series of nova explosions to allow the WD to gain
$\sim 0.6$ CHECK THIS \Msun\ needed for it to approach the
limiting Chandrasekhar mass~\citep{starrfieldetal2012}. As it approaches
the Chandrasekhar limit, conditions in the compressed core are right
to ignite the thermonuclear buring that will incinerate the star.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/FMBTI_v_Ni56Yield_plot.pdf}
\caption{\label{fig:compare}
The conversion of Ni56 to Iron group elements are more pronounced in my case. There are two assumptions as to why figure 6 is more pronounced in my paper then in Dons. 
First is that higher critical density leads to higher electron capture resulting in less Ni56 produced. Figure 4 shows that CO model has a stronger electron capture then the hybrid model. The second is that the central ignition leads to early burning at higher density. Both of these cases lead to more electron capture resulting in a larger difference in evolution between the models.
NEW: Production of 56Ni and mass burned to IGEs for CO (red) and
hybrid CONe (green) WD realizations. SAME AS DON'S FIG 18
}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{figures/compare_burned_mass_v2.png}
\caption{\label{fig:compare}
SAME AS DON'S FIGURE 19.
C/O blue hybrid red.
Note that one of the C/O simulations presented did not complete.
}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{figures/compare_ratio_v2.png}
\caption{\label{fig:compare_ratio}
Figure 8 shows the evolution of the materials for both models. It is determined that the CO model had the greatest amount of Ni56, then the other IGE materials, compared to the hybrid model.  
SAME AS DON'S FIGURE 20.
}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}
Thermonuclear (Type Ia) supernovae (\SNeIa) are bright stellar explosions 
thought to occur when approximately 1.0 \Msun\ of material composed principally 
of C and O burns under degenerate conditions. This class of supernovae is
know to synthesize much of the Fe-group elements found in the galaxy and
the light curves of these events have a spectial property that allows
their use as distance indicators for cosmological studies~\citep{phillips:absolute}
resulting in the discovery of the acceleration of the expansion of
the Universe and thus the inference of Dark 
Energy~\citep{riess.filippenko.ea:observational,
perlmutter.aldering.ea:measurements,leibundgut2001}. 
This special property of the light curve is thought to follow
from the fact that the source of luminosity, the radioactive decay
of \Ni{56}, synthesized by the thermonuclear burning, is also the
principle source of opacity~\citep{Pinto2001The-type-Ia-sup}.

@@

The single degenerate picture posits a white dwarf gaining mass
from a main-sequence companion. The process relies on a long
period of accretion combined with either steady burning or a 
series of nova explosions to allow the WD to gain at least
$\sim 0.4$ \Msun\ as needed for it to approach the
limiting Chandrasekhar mass~\citep{starrfieldetal2012}. As it approaches
the Chandrasekhar limit, conditions in the compressed core are right
to ignite the thermonuclear buring that will incinerate the star.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/FMBTI_v_Ni56Yield_plot.pdf}
\caption{\label{fig:conversion}
The conversion of Ni56 to Iron group elements are more pronounced in my case. There are two assumptions as to why figure 6 is more pronounced in my paper then in Dons. 
First is that higher critical density leads to higher electron capture resulting in less Ni56 produced. Figure 4 shows that CO model has a stronger electron capture then the hybrid model. The second is that the central ignition leads to early burning at higher density. Both of these cases lead to more electron capture resulting in a larger difference in evolution between the models.
NEW: Production of 56Ni and mass burned to IGEs for CO (red) and
hybrid CONe (green) WD realizations. SAME AS DON'S FIG 18
}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{figures/compare_ratio_v2.png}
\caption{\label{fig:compare_ratio}
Figure 8 shows the evolution of the materials for both models. It is determined that the CO model had the greatest amount of Ni56, then the other IGE materials, compared to the hybrid model.  
SAME AS DON'S FIGURE 19.
}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{figures/compare_burned_mass_v2.png}
\caption{\label{fig:compare_burned}
SAME AS DON'S FIGURE 20.
C/O blue hybrid red.
Note that one of the C/O simulations presented did not complete.
}
\end{figure}
